### 2025-04-30 paper/paper.tex
use latex template from conference

%% bare_conf.tex
%% V1.4b
%% 2015/08/26
%% by Michael Shell
%% See:
%% http://www.michaelshell.org/
%% for current contact information.
%%
%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% conference paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
% *** with production work. The IEEE's font choices and paper sizes can   ***
% *** trigger bugs that do not appear when using other class files.       ***                          ***
% The testflow support page is at:
% http://www.michaelshell.org/tex/testflow/

\documentclass[a4, conference]{IEEEtran}
\IEEEoverridecommandlockouts
% \usepackage{graphicx}
% \usepackage{cite}
% \usepackage{amsmath,amssymb,amsfonts}
% \usepackage{algorithmic}

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

%make sure in A4 paper
\usepackage[left=1.57cm,right=1.57cm,top=0.95cm,bottom=2.54cm]{geometry}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Bare Demo of IEEEtran.cls\\ for IEEE Conferences}

%\author{\small *No authors informations during review process.}
% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Michael Shell}
    \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
        Georgia Institute of Technology\\
        Atlanta, Georgia 30332--0250\\
        Email: http://www.michaelshell.org/contact.html}
    \and
    \IEEEauthorblockN{Homer Simpson}
    \IEEEauthorblockA{Twentieth Century Fox\\
        Springfield, USA\\
        Email: homer@thesimpsons.com}
    \and
    \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
    \IEEEauthorblockA{Starfleet Academy\\
        San Francisco, California 96678--2391\\
        Telephone: (800) 555--1212\\
        Fax: (888) 555--1212}}

% conference papers do not typically use \thanks and this command
% is locked out in conference mode. If really needed, such as for
% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
% after \documentclass

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
% 
%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
%Homer Simpson\IEEEauthorrefmark{2},
%James Kirk\IEEEauthorrefmark{3}, 
%Montgomery Scott\IEEEauthorrefmark{3} and
%Eldon Tyrell\IEEEauthorrefmark{4}}
%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

% use for special paper notices
%\IEEEspecialpapernotice{(Invited Paper)}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract
\begin{abstract}
    The abstract goes here.
\end{abstract}

% no keywords

% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle

\section{Introduction}
% no \IEEEPARstart
This demo file is intended to serve as a ``starter file''
for IEEE conference papers produced under \LaTeX\ using
IEEEtran.cls version 1.8b and later.
% You must have at least 2 lines in the paragraph with the drop letter
% (should never be an issue)
I wish you the best of success.

\hfill mds

\hfill August 26, 2015

\subsection{Subsection Heading Here}
Subsection text here. Cite \cite{xu2024chattf}

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

% An example of a floating figure using the graphicx package.
% Note that \label must occur AFTER (or within) \caption.
% For figures, \caption should occur after the \includegraphics.
% Note that IEEEtran v1.7 and later has special internal code that
% is designed to preserve the operation of \label within \caption
% even when the captionsoff option is in effect. However, because
% of issues like this, it may be the safest practice to put all your
% \label just after \caption rather than within \caption{}.
%
% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
% option should be used if it is desired that the figures are to be
% displayed while in draft mode.
%
%\begin{figure}[!t]
%\centering
%\includegraphics[width=2.5in]{myfigure}
% where an .eps filename suffix will be assumed under latex, 
% and a .pdf suffix will be assumed for pdflatex; or what has been declared
% via \DeclareGraphicsExtensions.
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure}

% Note that the IEEE typically puts floats only at the top, even when this
% results in a large percentage of a column being occupied by floats.

% An example of a double column floating figure using two subfigures.
% (The subfig.sty package must be loaded for this to work.)
% The subfigure \label commands are set within each subfloat command,
% and the \label for the overall figure must come after \caption.
% \hfil is used as a separator to get equal spacing.
% Watch out that the combined width of all the subfigures on a 
% line do not exceed the text width or a line break will occur.
%
%\begin{figure*}[!t]
%\centering
%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
%\label{fig_first_case}}
%\hfil
%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
%\label{fig_second_case}}
%\caption{Simulation results for the network.}
%\label{fig_sim}
%\end{figure*}
%
% Note that often IEEE papers with subfigures do not employ subfigure
% captions (using the optional argument to \subfloat[]), but instead will
% reference/describe all of them (a), (b), etc., within the main caption.
% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
% labels, the optional argument to \subfloat must be present. If a
% subcaption is not desired, just leave its contents blank,
% e.g., \subfloat[].

% An example of a floating table. Note that, for IEEE style tables, the
% \caption command should come BEFORE the table and, given that table
% captions serve much like titles, are usually capitalized except for words
% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
% and up, which are usually not capitalized unless they are the first or
% last word of the caption. Table text will default to \footnotesize as
% the IEEE normally uses this smaller font for tables.
% The \label must come after \caption as always.
%
% \begin{table}[!t]
% % increase table row spacing, adjust to taste
% \renewcommand{\arraystretch}{1.3}
% if using array.sty, it might be a good idea to tweak the value of
% \extrarowheight as needed to properly center the text within the cells
% \caption{An Example of a Table}
% \label{table_example}
% \centering
% % Some packages, such as MDW tools, offer better commands for making tables
% % than the plain LaTeX2e tabular which is used here.
% \begin{tabular}{|c||c|}
% \hline
% One & Two\\
% \hline
% Three & Four\\
% \hline
% \end{tabular}
% \end{table}

% Note that the IEEE does not put floats in the very first column
% - or typically anywhere on the first page for that matter. Also,
% in-text middle ("here") positioning is typically not used, but it
% is allowed and encouraged for Computer Society conferences (but
% not Computer Society journals). Most IEEE journals/conferences use
% top floats exclusively. 
% Note that, LaTeX2e, unlike IEEE journals/conferences, places
% footnotes above bottom floats. This can be corrected via the
% \fnbelowfloat command of the stfloats package.

\section{Conclusion}
The conclusion goes here.

% conference papers do not normally have an appendix

% use section* for acknowledgment
\section*{Acknowledgment}

The authors would like to thank...

% trigger a \newpage just before the given reference
% number - used to balance the columns on the last page
% adjust value as needed - may need to be readjusted if
% the document is modified later
%\IEEEtriggeratref{8}
% The "triggered" command can be changed if desired:
%\IEEEtriggercmd{\enlargethispage{-5in}}

% references section

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
%\begin{thebibliography}{1}

%\bibitem{IEEEhowto:kopka}
%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.

%\end{thebibliography}

%Use the following steps for compiling bibtex file:
%1. PDFLaTeX
%2. BibTeX
%3. PDFLaTeX
%4. PDFLaTeX

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,References}

% that's all folks
\end{document}

### 2025-04-30 paper/paper.tex
paper draft

@@
 \section{Introduction}
-% no \IEEEPARstart
-This demo file is intended to serve as a ``starter file''
-for IEEE conference papers produced under \LaTeX\ using
-IEEEtran.cls version 1.8b and later.
-% You must have at least 2 lines in the paragraph with the drop letter
-% (should never be an issue)
-I wish you the best of success.
 
-\hfill mds
+The increasing volume of information within cultural heritage institutions, such as museum archives, presents significant challenges for effective knowledge management and access.
+Knowledge graphs (KGs) offer a powerful solution by representing entities and their relationships in a structured and machine-readable format, enabling advanced functionalities like semantic search, data integration, and reasoning.
+In the cultural heritage domain, ontologies such as the CIDOC Conceptual Reference Model (CRM) [cite CIDOC CRM paper] provide a standardized framework for describing cultural objects, events, and their interrelationships, facilitating interoperability and data sharing across institutions.
 
-\hfill August 26, 2015
+Traditionally, the construction of ontology-conformant KGs is a labor-intensive process requiring expert knowledge in both the domain and the ontology.
+However, the recent advancements in Large Language Models (LLMs) have demonstrated their remarkable capabilities in understanding and generating human language.
+Notably, LLMs exhibit strong in-context learning abilities, allowing them to generalize over a wide range of language tasks, including complex information extraction, without the need for expensive fine-tuning.
+This opens up new possibilities for automated knowledge extraction and KG construction, and in this case specifically, processing unstructured textual data from museum archives and mapping the extracted information to the concepts and relationships defined in ontologies like the CIDOC-CRM.
 
-\subsection{Subsection Heading Here}
-Subsection text here. Cite \cite{xu2024chattf}
+This paper investigates the feasibility and effectiveness of using state-of-the-art LLMs to construct ontology-conformant knowledge graphs from museum archives, specifically focusing on the CIDOC-CRM.
+We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia.
+We construct a textual dataset from web pages dedicated to specific collections or exhibits, then employ an in-context learning approach to extract knowledge graph triplets according to a CIDOC-CRM-derived ontology.
+A key aspect of our approach is the integration of this ontology directly within a single-stage prompting process, with our hypothesis being knowledge graphs that are semantically richer and more accurate.
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+To evaluate the constructed knowledge graphs, we employ both intrinsic and extrinsic evaluation methods.
+The intrinsic evaluation measures the conformance of the generated graphs to the CIDOC-CRM ontology.
+The extrinsic evaluation is conducted through a Knowledge Base Question Answering (KBQA) task, where we use the knowledge graph as context for an LLM to answer questions related to the museum collections.
+This study aims to contribute to the growing body of research on leveraging LLMs and ontologies for knowledge graph generation, specifically in the cultural heritage domain, with the ultimate motivation of improving museum data management and access.
 
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure}
+\section{Related Work}
 
-% Note that the IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
+\subsection{Cultural Heritage Ontologies and Semantic Web}
 
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command,
-% and the \label for the overall figure must come after \caption.
-% \hfil is used as a separator to get equal spacing.
-% Watch out that the combined width of all the subfigures on a 
-% line do not exceed the text width or a line break will occur.
-%
-%\begin{figure*}[!t]
-%\centering
-%\subfloat[Case I]{\includegraphics[width=2.5in]{box}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{box}%
-%\label{fig_second_case}}
-%\caption{Simulation results for the network.}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat[]), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-% Be aware that for subfig.sty to generate the (a), (b), etc., subfigure
-% labels, the optional argument to \subfloat must be present. If a
-% subcaption is not desired, just leave its contents blank,
-% e.g., \subfloat[].
+In computer science, ontologies serve as formal, explicit specifications of a shared conceptualization for a domain of interest.
+They define the relevant classes (concepts), properties (attributes), and relationships between entities, along with axioms constraining their interpretation.
+Ontologies provide the semantic schema or backbone for Knowledge Graphs (KGs), which represent entities and their connections as nodes and edges.
+The common vocabulary and structure of ontologies ensures consistency, enables the integration of heterogeneous data, and facilitates semantic querying and logical reasoning over the interconnected information within a KG.
 
-% An example of a floating table. Note that, for IEEE style tables, the
-% \caption command should come BEFORE the table and, given that table
-% captions serve much like titles, are usually capitalized except for words
-% such as a, an, and, as, at, but, by, for, in, nor, of, on, or, the, to
-% and up, which are usually not capitalized unless they are the first or
-% last word of the caption. Table text will default to \footnotesize as
-% the IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-% \begin{table}[!t]
-% % increase table row spacing, adjust to taste
-% \renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-% \caption{An Example of a Table}
-% \label{table_example}
-% \centering
-% % Some packages, such as MDW tools, offer better commands for making tables
-% % than the plain LaTeX2e tabular which is used here.
-% \begin{tabular}{|c||c|}
-% \hline
-% One & Two\\
-% \hline
-% Three & Four\\
-% \hline
-% \end{tabular}
-% \end{table}
+The cultural heritage (CH) domain, characterized by its diverse institutions (museums, archives, libraries), varied collections, and heterogeneous documentation practices, faces significant challenges in data integration and interoperability.
+Ontologies play a critical role in addressing these issues by providing a common semantic framework.
+They act as a mediating layer, enabling disparate CH information sources—originally described using various metadata standards or local schemas—to be mapped, linked, and queried based on shared meaning, thereby facilitating integrated access and interdisciplinary research.
 
-% Note that the IEEE does not put floats in the very first column
-% - or typically anywhere on the first page for that matter. Also,
-% in-text middle ("here") positioning is typically not used, but it
-% is allowed and encouraged for Computer Society conferences (but
-% not Computer Society journals). Most IEEE journals/conferences use
-% top floats exclusively. 
-% Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the
-% \fnbelowfloat command of the stfloats package.
+The CIDOC Conceptual Reference Model (CIDOC-CRM, ISO 21127) is the preeminent standard ontology designed specifically for the integration of cultural heritage information.
+Developed over decades and grounded in the analysis of documentation practices across museums, libraries, and archives, CIDOC-CRM provides a formal, extensible semantic framework for describing the complex concepts and relationships inherent in CH data.
+Its event-centric modeling paradigm, which structures information around events linking actors, objects, places, and times, is particularly adept at capturing the rich contextual history crucial for understanding cultural objects and collections.
+Consequently, CIDOC-CRM serves as a vital tool for structuring knowledge extracted from diverse sources, including museum archives, and building interoperable cultural heritage knowledge graphs.
 
-\section{Conclusion}
-The conclusion goes here.
+\subsection{Ontology-Guided Knowledge Graph Generation}
 
-% conference papers do not normally have an appendix
+Ontology-guided or ontology-driven knowledge graph generation focuses on leveraging formal ontologies to guide the extraction of structured knowledge from unstructured or semi-structured text.
+By providing a predefined schema of concepts and relationships, ontologies ensure that the generated knowledge graphs are semantically consistent, well-structured, and aligned with a specific domain [Construction of Knowledge Graphs: Current State and Challenges].
+This approach is particularly relevant in domains like cultural heritage, where established ontologies like the CIDOC Conceptual Reference Model (CRM) offer a standardized framework for representing cultural objects, events, and their relationships.
 
-% use section* for acknowledgment
-\section*{Acknowledgment}
+The Text2KGBench benchmark [Text2KGBench: A Benchmark for Ontology-Driven Knowledge Graph Generation from Text] provides a comprehensive evaluation framework for ontology-driven knowledge graph generation.
+It uses an established ground truth to assess the quality of extracted knowledge graphs based on accuracy, ontology conformance and hallucination.
+Research utilizing this benchmark, such as the development of the specialized language model T5 [Domain Ontology-Driven Knowledge Graph Generation from Text], underscores the ongoing efforts to improve the accuracy and reliability of ontology-driven KG generation using advanced language models.
+These studies often experiment with different prompting strategies and model architectures to optimize the extraction process.
 
-The authors would like to thank...
+Several recent studies have explored the use of Large Language Models (LLMs) for knowledge graph generation.
+\cite{xu2024chattf} demonstrates an end-to-end intelligent question answering system for Chinese traditional folklore.
+Their approach utilizes a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from scraped web content about Chinese traditional folklore.
+[Transforming Indonesian Geography Education Books Into Knowledge Graphs Using ChatGPT LLMs] further illustrates the effectiveness of LLMs in extracting knowledge graphs, though this case used an ontology-free method.
+These examples highlight the potential of LLMs to construct ontology-conformant knowledge graphs in their respective domains.
 
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
+Furthermore [Assessing LLMs suitability for knowledge graph completion] investigates the suitability of LLMs for knowledge graph completion tasks, demonstrating that well-crafted prompts, particularly those employing in-context learning and chain-of-thought techniques, can yield significant improvements.
+This highlights the importance of effective prompting methodologies in guiding LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.
 
-% references section
+The potential of LLMs to understand and classify terms according to established ontologies like CIDOC CRM has also been shown by [Leveraging Large Language Models for Classification of Cultural Heritage Domain Terms: A Case Study on CIDOC CRM].
 
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://mirror.ctan.org/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-%\bibliographystyle{IEEEtran}
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-%\begin{thebibliography}{1}
+Our research focuses on the extraction of knowledge graphs from museum archives using an ontology derived from the CIDOC-CRM.
+Unlike the two-stage prompting approach employed by [ChatTf], we explore the effectiveness of a single-stage prompting method.
+Moreover, our study incorporates a comprehensive evaluation strategy that includes both intrinsic (ontology conformance) and extrinsic (KBQA task) metrics.
 
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+\section{Methods}
 
-%\end{thebibliography}
+The methodology is structured around the following key steps: ontology and dataset construction, knowledge graph generation (ontology-driven and ontology-free), and knowledge graph evaluation (intrinsic and extrinsic).
 
-%Use the following steps for compiling bibtex file:
-%1. PDFLaTeX
-%2. BibTeX
-%3. PDFLaTeX
-%4. PDFLaTeX
+\subsection{Ontology Construction}
+
+This study employs the CIDOC Conceptual Reference Model (CRM) [cite CIDOC-CRM standard] to structure the knowledge graphs extracted from cultural heritage texts.
+We derived a smaller ontology for use within our LLM prompting framework, specialized to our specific data source: Museum Nasional web pages describing collection items.
+While the primary reason was to save token costs, as the ontology must be supplied in each extraction prompt, this aligns with typical implementations where the full CRM is specialized for particular applications [cite].
+
+Our derived ontology profile was constructed by identifying the CIDOC-CRM classes and properties most relevant to describing museum objects, their history, and cultural context based on the expected content of the source material.
+The selection included core entities for physical objects, actors, places, and time-spans, key events related to object lifecycle and provenance (like production, acquisition, modification), and essential descriptive concepts (such as materials, types, titles, and dimensions).
+
+\subsection{Dataset Construction}
+
+The museum's official public website contains a wealth of information about its collection, with many exhibits and artifacts having dedicated articles.
+These articles were used to construct a dataset of textual information from the museum's collection, with each entry representing a complete article dedicated to a particular item.
+
+A custom Question-Answering (QA) dataset was also created to test knowledge about the information contained within the museum archives and to evaluate whether a knowledge graph contains the expected information from the source text.
+The QA dataset includes multiple-choice questions that assess both individual item-specific facts as well as comparative facts across multiple items.
+
+\subsection{Knowledge Graph Generation}
+
+We implemented two distinct approaches for generating knowledge graphs from the constructed dataset: an ontology-driven approach and a ontology-free approach.
+Both approaches utilized a single-stage prompting method.
+
+\subsubsection{Ontology-Guided}
+
+This approach leverages an ontology to guide the LLM in extracting structured information. The process consists of the following steps:
+
+\begin{enumerate}
+    \item Ontology Verbalization: The ontology is verbalized into a natural language description.
+    \item System Prompt Construction: A system prompt is constructed from the following elements
+          \begin{itemize}
+              \item A clear task description instructing the LLM to extract entities and relationships from the input text and represent them as a knowledge graph adhering to the provided ontology.
+              \item Example input-output pairs demonstrating the desired output format.
+              \item The verbalized ontology, appended at the end of the system prompt.
+          \end{itemize}
+    \item Chat History Initialization: The chat history is initialized with an example input and output to serve as an in-context learning mechanism.
+    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM.
+The response is parsed as a list of triplets and serialized as a JSONL file where each line contains the triplets extracted from a chunk.
+\end{enumerate}
+
+\subsubsection{Ontology-Free}
+
+The ontology-free approach aims to extract general knowledge graphs without specific guidance from the CIDOC-CRM ontology.
+It is nearly identical to the ontology-driven approach with the following key differences:
+
+\begin{itemize}
+    \item The task description instructed the LLM to identify entities and relationships relevant to museum collections and exhibits in the input text.
+    \item The example input-output pairs demonstrated the extraction of general relationships without mapping them to a specific ontology.
+    \item No verbalized ontology was included in the system prompt.
+\end{itemize}
+
+This ontology-free approach serves as a comparison point within the extrinsic evaluation, specifically to measure the impact of incorporating the ontology on KBQA performance, and indirectly, the accuracy of the knowledge graph.
 

### 2025-05-02 paper/paper.tex

@@
 \begin{document}
+\bstctlcite{IEEEexample:BSTcontrol}
 %
@@
 % Do not put math or special symbols in the title.
-\title{Bare Demo of IEEEtran.cls\\ for IEEE Conferences}
+\title{LLM-Driven CIDOC-CRM Knowledge Graph Extraction from Museum Archives}
 
@@
 % affiliations
-\author{\IEEEauthorblockN{Michael Shell}
-    \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
-        Georgia Institute of Technology\\
-        Atlanta, Georgia 30332--0250\\
-        Email: http://www.michaelshell.org/contact.html}
-    \and
-    \IEEEauthorblockN{Homer Simpson}
-    \IEEEauthorblockA{Twentieth Century Fox\\
-        Springfield, USA\\
-        Email: homer@thesimpsons.com}
-    \and
-    \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
-    \IEEEauthorblockA{Starfleet Academy\\
-        San Francisco, California 96678--2391\\
-        Telephone: (800) 555--1212\\
-        Fax: (888) 555--1212}}
+% \author{\IEEEauthorblockN{Michael Shell}
+%     \IEEEauthorblockA{School of Electrical and\\Computer Engineering\\
+%         Georgia Institute of Technology\\
+%         Atlanta, Georgia 30332--0250\\
+%         Email: http://www.michaelshell.org/contact.html}
+%     \and
+%     \IEEEauthorblockN{Homer Simpson}
+%     \IEEEauthorblockA{Twentieth Century Fox\\
+%         Springfield, USA\\
+%         Email: homer@thesimpsons.com}
+%     \and
+%     \IEEEauthorblockN{James Kirk\\ and Montgomery Scott}
+%     \IEEEauthorblockA{Starfleet Academy\\
+%         San Francisco, California 96678--2391\\
+%         Telephone: (800) 555--1212\\
+%         Fax: (888) 555--1212}}
 
@@
 
-The increasing volume of information within cultural heritage institutions, such as museum archives, presents significant challenges for effective knowledge management and access.
-Knowledge graphs (KGs) offer a powerful solution by representing entities and their relationships in a structured and machine-readable format, enabling advanced functionalities like semantic search, data integration, and reasoning.
-In the cultural heritage domain, ontologies such as the CIDOC Conceptual Reference Model (CRM) [cite CIDOC CRM paper] provide a standardized framework for describing cultural objects, events, and their interrelationships, facilitating interoperability and data sharing across institutions.
+The increasing volume of information within cultural heritage institutions, such as museum archives, presents significant challenges for effective knowledge management and access \cite{alexiev2018museum}.
+Knowledge graphs (KGs) offer a powerful solution by representing entities and their relationships in a structured and machine-readable format, enabling advanced functionalities like semantic search, data integration, and reasoning \cite{hofer2024constructionofknowledge}.
+These structured representations are crucial for unlocking the potential of cultural heritage data and facilitating its wider use.
+Initiatives such as Linked Open Data (LOD) exemplify the application of knowledge graph principles to enhance data integration and interoperability across cultural heritage institutions \cite{pedro2013connectingthesmithsonian,dutia2021heritageconnector}.
+These efforts often leverage ontologies such as the CIDOC Conceptual Reference Model \cite{doerr2005thecidoc} (CRM) to provide a shared framework for describing cultural objects, events, and their interrelationships, facilitating interoperability and data sharing across institutions.
 
-Traditionally, the construction of ontology-conformant KGs is a labor-intensive process requiring expert knowledge in both the domain and the ontology.
-However, the recent advancements in Large Language Models (LLMs) have demonstrated their remarkable capabilities in understanding and generating human language.
-Notably, LLMs exhibit strong in-context learning abilities, allowing them to generalize over a wide range of language tasks, including complex information extraction, without the need for expensive fine-tuning.
-This opens up new possibilities for automated knowledge extraction and KG construction, and in this case specifically, processing unstructured textual data from museum archives and mapping the extracted information to the concepts and relationships defined in ontologies like the CIDOC-CRM.
+Traditionally, the construction of ontology-conformant KGs is a labor-intensive process requiring expert knowledge in both the domain and the ontology \cite{hofer2024constructionofknowledge}.
+However, the recent advancements in Large Language Models (LLMs) have demonstrated remarkable in-context learning abilities, allowing them to generalize over a wide range of language tasks, including complex information extraction \cite{remadi2024topromptornottoprompt}, without the need for expensive fine-tuning.
+This opens up new possibilities for automated knowledge extraction and KG construction \cite{ibrahim2024asurveyonaugmentingknowledgegraphs,zhu2024llmsknowledgegraphconstruction}, and in this case specifically, processing unstructured textual data from museum archives and mapping the extracted information to the concepts and relationships defined in ontologies like the CIDOC-CRM \cite{bruseker2017culturalheritagedatamanagement}.
 
-This paper investigates the feasibility and effectiveness of using state-of-the-art LLMs to construct ontology-conformant knowledge graphs from museum archives, specifically focusing on the CIDOC-CRM.
-We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia.
-We construct a textual dataset from web pages dedicated to specific collections or exhibits, then employ an in-context learning approach to extract knowledge graph triplets according to a CIDOC-CRM-derived ontology.
+This paper investigates the feasibility and effectiveness of using LLMs to construct CIDOC-CRM knowledge graphs from museum archives.
+We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia, where we construct a textual dataset from web pages dedicated to specific collections or exhibits, then employ an in-context learning approach to extract knowledge graph triplets according to a CIDOC-CRM-derived ontology.
 A key aspect of our approach is the integration of this ontology directly within a single-stage prompting process, with our hypothesis being knowledge graphs that are semantically richer and more accurate.
 
-To evaluate the constructed knowledge graphs, we employ both intrinsic and extrinsic evaluation methods.
+To evaluate the constructed knowledge graphs, we employ both an intrinsic and extrinsic evaluation method.
 The intrinsic evaluation measures the conformance of the generated graphs to the CIDOC-CRM ontology.
 The extrinsic evaluation is conducted through a Knowledge Base Question Answering (KBQA) task, where we use the knowledge graph as context for an LLM to answer questions related to the museum collections.
-This study aims to contribute to the growing body of research on leveraging LLMs and ontologies for knowledge graph generation, specifically in the cultural heritage domain, with the ultimate motivation of improving museum data management and access.
+This study aims to contribute to the growing body of research on leveraging LLMs and ontologies for knowledge graph generation, specifically in the cultural heritage domain, with the motivation of improving the interoperability and accessibility of cultural heritage information across institutions.
 
@@
 Ontologies provide the semantic schema or backbone for Knowledge Graphs (KGs), which represent entities and their connections as nodes and edges.
-The common vocabulary and structure of ontologies ensures consistency, enables the integration of heterogeneous data, and facilitates semantic querying and logical reasoning over the interconnected information within a KG.
 
-The cultural heritage (CH) domain, characterized by its diverse institutions (museums, archives, libraries), varied collections, and heterogeneous documentation practices, faces significant challenges in data integration and interoperability.
-Ontologies play a critical role in addressing these issues by providing a common semantic framework.
-They act as a mediating layer, enabling disparate CH information sources—originally described using various metadata standards or local schemas—to be mapped, linked, and queried based on shared meaning, thereby facilitating integrated access and interdisciplinary research.
-
-The CIDOC Conceptual Reference Model (CIDOC-CRM, ISO 21127) is the preeminent standard ontology designed specifically for the integration of cultural heritage information.
-Developed over decades and grounded in the analysis of documentation practices across museums, libraries, and archives, CIDOC-CRM provides a formal, extensible semantic framework for describing the complex concepts and relationships inherent in CH data.
-Its event-centric modeling paradigm, which structures information around events linking actors, objects, places, and times, is particularly adept at capturing the rich contextual history crucial for understanding cultural objects and collections.
+The CIDOC Conceptual Reference Model \cite{doerr2005thecidoc} (CIDOC-CRM, ISO 21127) is a major foundation ontology designed for the integration of cultural heritage information.
+Its event-centric modeling paradigm, which structures information around events linking actors, objects, places, and times, captures the rich contextual history crucial for understanding cultural objects and collections.
 Consequently, CIDOC-CRM serves as a vital tool for structuring knowledge extracted from diverse sources, including museum archives, and building interoperable cultural heritage knowledge graphs.
@@
 
-Ontology-guided or ontology-driven knowledge graph generation focuses on leveraging formal ontologies to guide the extraction of structured knowledge from unstructured or semi-structured text.
-By providing a predefined schema of concepts and relationships, ontologies ensure that the generated knowledge graphs are semantically consistent, well-structured, and aligned with a specific domain [Construction of Knowledge Graphs: Current State and Challenges].
-This approach is particularly relevant in domains like cultural heritage, where established ontologies like the CIDOC Conceptual Reference Model (CRM) offer a standardized framework for representing cultural objects, events, and their relationships.
-
-The Text2KGBench benchmark [Text2KGBench: A Benchmark for Ontology-Driven Knowledge Graph Generation from Text] provides a comprehensive evaluation framework for ontology-driven knowledge graph generation.
-It uses an established ground truth to assess the quality of extracted knowledge graphs based on accuracy, ontology conformance and hallucination.
-Research utilizing this benchmark, such as the development of the specialized language model T5 [Domain Ontology-Driven Knowledge Graph Generation from Text], underscores the ongoing efforts to improve the accuracy and reliability of ontology-driven KG generation using advanced language models.
-These studies often experiment with different prompting strategies and model architectures to optimize the extraction process.
+Ontology-guided knowledge graph generation focuses on leveraging formal ontologies to guide the extraction of structured knowledge from unstructured or semi-structured text.
+By providing a predefined schema of concepts and relationships, ontologies ensure that the generated knowledge graphs are semantically consistent, well-structured, and aligned with a specific domain \cite{hofer2024constructionofknowledge}.
 
 Several recent studies have explored the use of Large Language Models (LLMs) for knowledge graph generation.
-\cite{xu2024chattf} demonstrates an end-to-end intelligent question answering system for Chinese traditional folklore.
-Their approach utilizes a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from scraped web content about Chinese traditional folklore.
-[Transforming Indonesian Geography Education Books Into Knowledge Graphs Using ChatGPT LLMs] further illustrates the effectiveness of LLMs in extracting knowledge graphs, though this case used an ontology-free method.
-These examples highlight the potential of LLMs to construct ontology-conformant knowledge graphs in their respective domains.
-
-Furthermore [Assessing LLMs suitability for knowledge graph completion] investigates the suitability of LLMs for knowledge graph completion tasks, demonstrating that well-crafted prompts, particularly those employing in-context learning and chain-of-thought techniques, can yield significant improvements.
-This highlights the importance of effective prompting methodologies in guiding LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.
-
-The potential of LLMs to understand and classify terms according to established ontologies like CIDOC CRM has also been shown by [Leveraging Large Language Models for Classification of Cultural Heritage Domain Terms: A Case Study on CIDOC CRM].
+Xu et al \cite{xu2024chattf} utilize a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from textual data about Chinese traditional folklore.
+Beyond the cultural heritage domain, Van Cauter and Yakovets \cite{cauter2024ontology} demonstrate KG generation from maintenance short texts, while Carriero et al \cite{carriero2025humanevaluationofprocedural} construct KGs from procedural texts such as recipes or manuals.
+These studies often experiment with different prompting strategies to optimize the extraction process.
+In particular, Iga et al \cite{iga2024assessllm} demonstrate the impact of well-crafted prompts, specifically those employing in-context learning and chain-of-thought techniques, in yielding significant improvements.
+This highlights the importance of effective prompting methodologies to guide LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.
 
 Our research focuses on the extraction of knowledge graphs from museum archives using an ontology derived from the CIDOC-CRM.
-Unlike the two-stage prompting approach employed by [ChatTf], we explore the effectiveness of a single-stage prompting method.
+Unlike the two-stage prompting approach employed by \cite{xu2024chattf}, we explore the effectiveness of a single-stage prompting method.
 Moreover, our study incorporates a comprehensive evaluation strategy that includes both intrinsic (ontology conformance) and extrinsic (KBQA task) metrics.
@@
 
-The methodology is structured around the following key steps: ontology and dataset construction, knowledge graph generation (ontology-driven and ontology-free), and knowledge graph evaluation (intrinsic and extrinsic).
+The methodology consists of the following key steps: ontology and dataset construction, knowledge graph generation (ontology-driven and ontology-free), and knowledge graph evaluation (intrinsic and extrinsic).
 
@@
 
-This study employs the CIDOC Conceptual Reference Model (CRM) [cite CIDOC-CRM standard] to structure the knowledge graphs extracted from cultural heritage texts.
-We derived a smaller ontology for use within our LLM prompting framework, specialized to our specific data source: Museum Nasional web pages describing collection items.
-While the primary reason was to save token costs, as the ontology must be supplied in each extraction prompt, this aligns with typical implementations where the full CRM is specialized for particular applications [cite].
+This study employs the CIDOC Conceptual Reference Model (CRM) to structure the knowledge graphs extracted from cultural heritage texts.
+Due to the sheer size and complexity of the CIDOC-CRM, we derived a smaller ontology for use within our LLM prompting framework.
 
-Our derived ontology profile was constructed by identifying the CIDOC-CRM classes and properties most relevant to describing museum objects, their history, and cultural context based on the expected content of the source material.
+This ontology was constructed by identifying the CIDOC-CRM classes and properties most relevant to describing museum objects, their history, and cultural context based on the expected content of the source material.
 The selection included core entities for physical objects, actors, places, and time-spans, key events related to object lifecycle and provenance (like production, acquisition, modification), and essential descriptive concepts (such as materials, types, titles, and dimensions).
@@
 A custom Question-Answering (QA) dataset was also created to test knowledge about the information contained within the museum archives and to evaluate whether a knowledge graph contains the expected information from the source text.
-The QA dataset includes multiple-choice questions that assess both individual item-specific facts as well as comparative facts across multiple items.
+The QA dataset includes 200 questions: 185 questions about individual item-specific facts, and 15 questions about comparative facts across multiple items.
 
@@
 
-We implemented two distinct approaches for generating knowledge graphs from the constructed dataset: an ontology-driven approach and a ontology-free approach.
+In addition to an ontology-guided graph generation approach, we also implement an ontology-free approach in order to evaluate the impact of ontology guidance on information quality via KBQA evaluation.
 Both approaches utilized a single-stage prompting method.
+The prompts were constructed based on level 4 of the TELeR prompt taxonomy \cite{santu2023telergeneraltaxonomyllm}, consisting of a high-level goal description, a bulleted list of sub-tasks, as well as input/output examples to facilitate in-context learning.
 
@@
 \begin{enumerate}
-    \item Ontology Verbalization: The ontology is verbalized into a natural language description.
-    \item System Prompt Construction: A system prompt is constructed from the following elements
+    \item Ontology Verbalization: The ontology is verbalized into a natural language description. We use the 24037 Erlangen CRM implementation of CIDOC-CRM 7.1.3.
+    \item System Prompt Construction: A system prompt is constructed from the following elements:
           \begin{itemize}
               \item A clear task description instructing the LLM to extract entities and relationships from the input text and represent them as a knowledge graph adhering to the provided ontology.
-              \item Example input-output pairs demonstrating the desired output format.
+              \item Examples demonstrating desired output format.
               \item The verbalized ontology, appended at the end of the system prompt.
@@
     \item Chat History Initialization: The chat history is initialized with an example input and output to serve as an in-context learning mechanism.
-    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM.
-The response is parsed as a list of triplets and serialized as a JSONL file where each line contains the triplets extracted from a chunk.
+    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM. The response is parsed as a list of triplets.
 \end{enumerate}
@@
 
-This ontology-free approach serves as a comparison point within the extrinsic evaluation, specifically to measure the impact of incorporating the ontology on KBQA performance, and indirectly, the accuracy of the knowledge graph.
+This ontology-free approach serves as a comparison point within the extrinsic evaluation, specifically to measure the impact of incorporating the ontology on the graph's accuracy via KBQA performance.
+
+\subsection{Knowledge Graph Evaluation}
+
+To evaluate the constructed knowledge graphs, we employ both intrinsic and extrinsic evaluation methods.
+The intrinsic evaluation measures the conformance of the generated graphs to the CIDOC-CRM ontology.
+The extrinsic evaluation is conducted through a Knowledge Base Question Answering (KBQA) task, where we use the knowledge graph as context for an LLM to answer questions related to the museum collections.
+
+\subsubsection{Intrinsic: Ontology Conformance}
+
+This metric aims to validate that the extracted subject-predicate-object triplets are consistent with the provided ontology.
+Building upon the Ontology Conformance (OC) metric from Text2KGBench \cite{mihindukulasooriya2023text2kgbench}, our approach not only checks if the predicate (property) is defined in the ontology, but also verifies that the subject and object of each triplet are valid instances of the domain and range specified for that particular property within the CIDOC-CRM.
+
+\subsubsection{Extrinsic: Knowledge Base Question Answering (KBQA) Task}
+
+In the absence of a "ground truth" graph, we evaluated KG accuracy by conducting an extrinsic evaluation using a Knowledge Base Question Answering (KBQA) task.
+
+This task involved a curated set of 200 factual questions derived directly from the Museum Nasional archive dataset.
+The question set comprised 185 "single-item" questions, each focusing on specific details within individual item descriptions, with at least one question for each artifact/item in the source archives.
+Additionally, 15 more complex "multi-item" questions were created which require the model to synthesize information across multiple items to arrive at the correct answer.
+
+For each model tested, we produced two knowledge graphs: one constructed without explicit ontology guidance and another guided by our CIDOC-CRM-derived ontology.
+These two graphs, along with a no-context "blank" baseline, were evaluated on the KBQA task.
+The blank baseline involved querying the LLM directly with the questions, without providing any knowledge graph as context, serving as a control to gauge the model's inherent knowledge about the museum's collection.
+
+The KBQA task was executed by constructing a system prompt.
+For the ontology-guided and ontology-free knowledge graphs, the prompt included a verbalized representation of the respective graph as the primary context, instructing the LLM to answer each multiple-choice question (with options "A", "B", "C", or "D") using only the information provided in the context.
+Meanwhile, the no-context baseline prompt simply presented the question to the LLM without any additional context.
+The score for each question
+
+The overall performance for each evaluated knowledge graph and the no-context baseline was then calculated as the percentage of questions answered correctly, resulting in a "single-item", "multi-item", and an overall accuracy score (out of 100).
+The final score for each question is determined by a "best-of-three" approach, requiring the LLM to answer correctly in at least two of three attempts.
+
+This methodology allowed us to quantitatively assess the extent to which the generated knowledge graphs, particularly the ontology-guided one, enhanced the LLM's ability to accurately retrieve and reason over information from the museum archives.
+
+\section{Experiment}
+
+We perform ontology-free and ontology-guided graph extraction on open-weight LLMs of various sizes, producing two graphs for each model.
+Specifically, we conducted experiments using Llama 3 \cite{grattafiori2024llama3herdmodels} (3B and 8B) and Qwen 2.5 \cite{qwen2025qwen25technicalreport} (3B and 7B) deployed on local hardware, and DeepSeek \cite{deepseekai2024deepseekv3technicalreport,deepseekai2025deepseekr1incentivizingreasoningcapability} models (V3 and R1) accessed via API endpoints.
+Each graph is then evaluated for ontology conformance and KBQA performance.
+
+\begin{table}[h]
+    \centering
+    \caption{Models for Graph Generation}
+    \label{tab:model_deployment}
+    \begin{tabular}{ll}
+        \hline
+        Model        & Deployment         \\
+        \hline
+        Qwen 2.5 3B  & Ollama on RTX 3060 \\
+        Llama 3.2 3B & Ollama on RTX 3060 \\
+        Qwen 2.5 7B  & LM Studio          \\
+        Llama 3.1 8B & LM Studio          \\
+        DeepSeek V3  & DeepSeek Platform  \\
+        DeepSeek R1  & DeepSeek Platform  \\
+        \hline
+    \end{tabular}
+\end{table}
+
+KBQA evaluation was performed on Deepseek V3 via DeepSeek Platform.
+
+\section{Results}
+
+\subsection{Ontology Conformance Evaluation}
+
+\begin{table}[h]
+    \centering
+    \caption{Ontology Conformance}
+    \label{tab:oc_percent}
+    \begin{tabular}{|l|c|c|c|}
+        \hline
+        Graph       & Total Triplets & Valid Triplets & Score          \\
+        \hline
+        Qwen 2.5 3B & 364            & 177            & 48.63          \\
+        \hline
+        Llama 3 3B  & 417            & 218            & 52.28          \\
+        \hline
+        Qwen 2.5 7B & 443            & 225            & 50.79          \\
+        \hline
+        Llama 3 8B  & 519            & 332            & 63.97          \\
+        \hline
+        DeepSeek V3 & 630            & 596            & 94.6           \\
+        \hline
+        DeepSeek R1 & 630            & 622            & \textbf{98.73} \\
+        \hline
+    \end{tabular}
+\end{table}
+
+Table \ref{tab:oc_percent} presents the ontology conformance scores for the knowledge graphs generated by the LLMs.
+Achieving high ontology conformance is a fundamental requirement for any viable method aiming to construct CIDOC-CRM knowledge graphs, as a knowledge graph that does not adhere to the ontology's specifications lacks the semantic consistency necessary for downstream use cases.
+
+The results clearly illustrate a positive correlation between the parameter size of the language model and the resulting ontology conformance.
+Smaller models, such as Qwen 2.5 3B (48.63\%) and Llama 3 3B (52.28\%), demonstrated considerably low conformance rates.
+Increasing the parameter count led to improvements, as seen with Qwen 2.5 7B (50.79\%) and Llama 3 8B (63.97\%).
+
+However, a significant performance gap exists between these smaller models and the larger DeepSeek models.
+DeepSeek V3 achieved a high score of 94.6\%, and DeepSeek R1 reached an impressive \textbf{98.73\%} ontology conformance.
+This suggests that accurately interpreting and applying ontology constraints remains a considerably more challenging task for smaller language models.
+
+\subsection{KBQA Evaluation}
+
+\begin{table}[h]
+    \centering
+    \caption{KBQA score (overall)}
+    \label{tab:qa_percent}
+    \begin{tabular}{|l|c|c|}
+        \hline
+        Graph       & Ontology-Free               & Ontology-Guided \\
+        \hline
+        Blank       & \multicolumn{2}{|c|}{60.50}                   \\
+        \hline
+        Qwen 2.5 3B & 73.50                       & 68.50           \\
+        \hline
+        Llama 3 3B  & 79.50                       & 78.00           \\
+        \hline
+        Qwen 2.5 7B & 95.50                       & 87.50           \\
+        \hline
+        Llama 3 8B  & 92.00                       & 90.50           \\
+        \hline
+        Deepseek V3 & \textbf{98.00}              & \textbf{97.50}  \\
+        \hline
+        Deepseek R1 & 97.50                       & 95.00           \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[h]
+    \centering
+    \caption{KBQA score (single item)}
+    \label{tab:qa_percent_single}
+    \begin{tabular}{|l|c|c|}
+        \hline
+        Graph       & Ontology-Free               & Ontology-Guided \\
+        \hline
+        Blank       & \multicolumn{2}{|c|}{62.16}                   \\
+        \hline
+        Qwen 2.5 3B & 72.97                       & 67.57           \\
+        \hline
+        Llama 3 3B  & 80.54                       & 78.92           \\
+        \hline
+        Qwen 2.5 7B & 95.68                       & 89.19           \\
+        \hline
+        Llama 3 8B  & 94.05                       & 91.89           \\
+        \hline
+        Deepseek V3 & \textbf{100}                & \textbf{98.38}  \\
+        \hline
+        Deepseek R1 & 98.92                       & 96.22           \\
+        \hline
+    \end{tabular}
+\end{table}
+
+\begin{table}[h]
+    \centering
+    \caption{KBQA score (multi item)}
+    \label{tab:qa_percent_multi}
+    \begin{tabular}{|l|c|c|}
+        \hline
+        Graph       & Ontology-Free            & Ontology-Guided \\
+        \hline
+        Blank       & \multicolumn{2}{|c|}{40}                   \\
+        \hline
+        Qwen 2.5 3B & 80                       & 80              \\
+        \hline
+        Llama 3 3B  & 66.67                    & 66.67           \\
+        \hline
+        Qwen 2.5 7B & \textbf{93.33}           & 66.67           \\
+        \hline
+        Llama 3 8B  & 66.67                    & 73.33           \\
+        \hline
+        Deepseek V3 & 73.33                    & \textbf{86.67}  \\
+        \hline
+        Deepseek R1 & 80                       & 80              \\
+        \hline
+    \end{tabular}
+\end{table}
+
+The results of the Knowledge Base Question Answering (KBQA) task, designed to evaluate the practical utility of the generated knowledge graphs, are presented in Tables \ref{tab:qa_percent}, \ref{tab:qa_percent_single}, and \ref{tab:qa_percent_multi}.
+These tables report the overall accuracy, the accuracy on single-item questions, and the accuracy on multi-item questions, respectively, for both ontology-free and ontology-guided knowledge graphs generated by each tested LLM, in addition to the no-context "blank" test.
+
+A notable observation is the relatively high performance of the "Blank" baseline across all question types, particularly on the single-item questions (62.16\% accuracy).
+This suggests that the LLMs, even without access to the generated knowledge graphs, possess a significant amount of information relevant to the Museum Nasional collection, potentially acquired during their pretraining.
+It is also possible that a subset of the questions could be answered through general reasoning capabilities without specific knowledge of the museum's data.
+The lower performance of the "Blank" baseline on multi-item questions (40\% accuracy) indicates that these more complex queries necessitate the integration of information, which the models struggle with in the absence of context.
+
+The general trend on KBQA results is that larger models tend to yield better KBQA results.
+This aligns with the findings from the ontology conformance evaluation, suggesting that increased model capacity contributes to improved information extraction and reasoning capabilities.
+However, compared to ontology conformance, the differences are not so extreme.
+This suggests that while smaller models struggle to reason around ontology constraints, they still have reasonable capability to extract information.
+
+Comparing the ontology-free and guided approaches, while ontology-free graphs achieve marginally scores, the overall difference remains small.
+This close performance between ontology-free and ontology-guided graphs has important implications.
+It suggests that while enforcing ontological structure does not impede the extraction of answerable information, it also doesn't provide a substantial boost in question-answering accuracy in this specific evaluation setting.
+This could be due to several factors, including the nature of the questions asked, the effectiveness of the ontology integration in the prompting process, or the inherent ability of the LLMs to extract relevant information even without explicit ontological guidance.
+
+\section{Conclusion}
 

### 2025-05-02 paper/paper.tex
paper: conclusiona and abstract

@@
 \begin{abstract}
-    The abstract goes here.
+    The increasing volume of information in cultural heritage institutions necessitates effective knowledge management solutions.
+Knowledge graphs (KGs), particularly those aligned with ontologies like the CIDOC Conceptual Reference Model (CIDOC-CRM), offer a powerful framework for structuring and accessing this data.
+However, traditional KG construction is labor-intensive.
+Recent advancements in Large Language Models (LLMs) present an opportunity for automated knowledge extraction.
+This paper investigates the feasibility and effectiveness of using LLMs for constructing CIDOC-CRM knowledge graphs from museum archives, employing a single-stage in-context learning approach guided by a derived ontology.
+We present a case study using the online archives of the Museum Nasional in Jakarta, Indonesia.
+The constructed knowledge graphs are evaluated using both intrinsic (ontology conformance) and extrinsic (Knowledge Base Question Answering - KBQA) metrics.
+
+    Evaluation results demonstrate that larger LLMs achieve substantially higher ontology conformance (exceeding 90\%), which is essential for ensuring semantic consistency.
+KBQA evaluation revealed a notable baseline performance by LLMs without explicit graph context, suggesting inherent knowledge.
+While graphs by larger models generally yielded higher KBQA scores, the performance difference between ontology-guided and ontology-free generated graphs was found to be marginal.
+This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the necessity for more sophisticated evaluation benchmarks to comprehensively assess CIDOC-CRM KG generation methods.
 \end{abstract}
@@
 
+This paper explored the use of Large Language Models for automatically constructing knowledge graphs from museum archives, focusing on the CIDOC-CRM ontology.
+Our case study, conducted on the Museum Nasional in Jakarta's online archives, demonstrated the feasibility of a single-stage prompting approach for extracting structured information as knowledge graph triplets.
+
+Our findings indicate a disparity in LLM capabilities: while smaller models can extract factual information, adhering to the complex constraints of the CIDOC-CRM ontology is only achievable by larger models.
+This highlights the enhanced capacity of larger LLMs for accurate ontological interpretation and application.
+Ultimately, this research underscores the significant potential of LLMs to generate meaningful, ontology-conformant knowledge graphs, offering a promising route for cultural heritage institutions to improve data management and access.
+
+The practical value of the generated knowledge graphs was evaluated through a Knowledge Base Question Answering task.
+Interestingly, LLMs exhibited surprisingly strong baseline performance without the generated graphs, suggesting pre-existing knowledge of the museum's collections.
+While larger models showed improved KBQA accuracy, the impact of ontology guidance on this task was limited.
+This suggests that while crucial for semantic validity, ontology integration didn't significantly hinder factual information extraction in this evaluation.
+This also emphasizes the growing need for more sophisticated benchmarks that can better assess the benefits of ontology integration in KG generation from text.
+
+In conclusion, our study contributes to the growing field exploring the synergy of LLMs, ontologies, and knowledge graphs within the cultural heritage domain.
+The high ontology conformance achieved by larger LLMs demonstrates the potential for creating structurally sound CIDOC-CRM knowledge graphs automatically.
+The KBQA results indicate their utility in augmenting information retrieval.
+Future research should focus on refining ontology integration techniques, exploring benefits in complex reasoning, and evaluating scalability across diverse archives.
+The overarching aim is to leverage these technologies to significantly enhance cultural heritage data management, accessibility, and research.
+
 \bibliographystyle{IEEEtran}

### 2025-05-02 paper/paper.tex
paper: fix hanging sentence
paper: mention dataset size, JSON parse, valid triplet %

@@
 The museum's official public website contains a wealth of information about its collection, with many exhibits and artifacts having dedicated articles.
-These articles were used to construct a dataset of textual information from the museum's collection, with each entry representing a complete article dedicated to a particular item.
+These articles were used to construct a dataset of textual information from the museum's collection.
+We collected 40 such articles such that each entry of the dataset represented a complete article dedicated to a particular item.
 
@@
     \item Chat History Initialization: The chat history is initialized with an example input and output to serve as an in-context learning mechanism.
-    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM. The response is parsed as a list of triplets.
+    \item Triplet Extraction: The system prompt, chat history and text chunk are sent to the LLM. The response is parsed as a JSON list of triplets.
 \end{enumerate}
@@
 Meanwhile, the no-context baseline prompt simply presented the question to the LLM without any additional context.
-The score for each question
 
@@
         \hline
-        Graph       & Total Triplets & Valid Triplets & Score          \\
+        Graph       & Total Triplets & Valid Triplets & Valid Triplets (\%) \\
         \hline

### 2025-05-02 paper/paper.tex
paper: revise IV experiment and VI conclusion

@@
 \section{Introduction}
+\label{sec:introduction}
 
@@
 \section{Related Work}
+\label{sec:related_work}
 
@@
 \section{Methods}
+\label{sec:methods}
 
@@
 \section{Experiment}
-
-We perform ontology-free and ontology-guided graph extraction on open-weight LLMs of various sizes, producing two graphs for each model.
-Specifically, we conducted experiments using Llama 3 \cite{grattafiori2024llama3herdmodels} (3B and 8B) and Qwen 2.5 \cite{qwen2025qwen25technicalreport} (3B and 7B) deployed on local hardware, and DeepSeek \cite{deepseekai2024deepseekv3technicalreport,deepseekai2025deepseekr1incentivizingreasoningcapability} models (V3 and R1) accessed via API endpoints.
-Each graph is then evaluated for ontology conformance and KBQA performance.
+\label{sec:experiment}
 
@@
     \centering
-    \caption{Models for Graph Generation}
+    \caption{Models used for Knowledge Graph Generation} % Updated caption slightly
     \label{tab:model_deployment}
@@
 
-KBQA evaluation was performed on Deepseek V3 via DeepSeek Platform.
+We conducted experiments involving two main stages: \textbf{knowledge graph generation} and \textbf{knowledge graph evaluation}.
+
+For the knowledge graph generation stage, we produced two sets of graphs from the collected textual dataset: one using an ontology-free approach and one using an ontology-guided approach.
+This generation was performed using open-weight LLMs of various sizes, specifically Llama 3 \cite{grattafiori2024llama3herdmodels} (3B and 8B) and Qwen 2.5 \cite{qwen2025qwen25technicalreport} (3B and 7B) deployed on local hardware, and DeepSeek \cite{deepseekai2024deepseekv3technicalreport,deepseekai2025deepseekr1incentivizingreasoningcapability} models (V3 and R1) accessed via API endpoints (Table \ref{tab:model_deployment}).
+In total, we generated twelve knowledge graphs: an ontology-free and an ontology-guided graph for each of the six listed models.
+
+These constructed knowledge graphs were then subjected to evaluation.
+The intrinsic evaluation (Ontology Conformance), as described in Section \ref{sec:methods}, was performed on the ontology-guided graphs generated by each model.
+For the extrinsic evaluation, the Knowledge Base Question Answering (KBQA) task was conducted.
+In this task, the DeepSeek V3 model, accessed via the DeepSeek Platform, was employed as the question-answering model.
+For each question in the curated dataset, the DeepSeek V3 model was prompted to provide an answer based on one of the following contexts:
+\begin{itemize}
+    \item A verbalized representation of the ontology-free knowledge graph generated by one of the six distinct models
+    \item A verbalized representation of the ontology-guided knowledge graph generated by one of the six distinct models
+    \item A blank context, where the DeepSeek V3 model received only the question without any generated graph information
+\end{itemize}
+
+This setup allowed us to evaluate the question-answering performance when leveraging graphs generated by different models and approaches, comparing them against each other as well as a no-context "blank" scenario.
 
@@
         \hline
-        Deepseek V3 & \textbf{98.00}              & \textbf{97.50}  \\
+        DeepSeek V3 & \textbf{98.00}              & \textbf{97.50}  \\
         \hline
-        Deepseek R1 & 97.50                       & 95.00           \\
+        DeepSeek R1 & 97.50                       & 95.00           \\
         \hline
@@
         \hline
-        Deepseek V3 & \textbf{100}                & \textbf{98.38}  \\
+        DeepSeek V3 & \textbf{100}                & \textbf{98.38}  \\
         \hline
-        Deepseek R1 & 98.92                       & 96.22           \\
+        DeepSeek R1 & 98.92                       & 96.22           \\
         \hline
@@
         \hline
-        Deepseek V3 & 73.33                    & \textbf{86.67}  \\
+        DeepSeek V3 & 73.33                    & \textbf{86.67}  \\
         \hline
-        Deepseek R1 & 80                       & 80              \\
+        DeepSeek R1 & 80                       & 80              \\
         \hline
@@
 
-Comparing the ontology-free and guided approaches, while ontology-free graphs achieve marginally scores, the overall difference remains small.
+Comparing the ontology-free and guided approaches, while ontology-free graphs achieve marginally higher scores, the overall difference remains small.
 This close performance between ontology-free and ontology-guided graphs has important implications.
-It suggests that while enforcing ontological structure does not impede the extraction of answerable information, it also doesn't provide a substantial boost in question-answering accuracy in this specific evaluation setting.
+It suggests that while enforcing ontological structure does not impede the extraction of answerable information, it also doesn't provide a substantial boost in question-answering accuracy, at least in this specific evaluation setting.
 This could be due to several factors, including the nature of the questions asked, the effectiveness of the ontology integration in the prompting process, or the inherent ability of the LLMs to extract relevant information even without explicit ontological guidance.
@@
 This suggests that while crucial for semantic validity, ontology integration didn't significantly hinder factual information extraction in this evaluation.
-This also emphasizes the growing need for more sophisticated benchmarks that can better assess the benefits of ontology integration in KG generation from text.
+This also emphasizes the growing need for more sophisticated benchmarks that can better assess the quality of CIDOC-CRM knowledge graphs.
 
-In conclusion, our study contributes to the growing field exploring the synergy of LLMs, ontologies, and knowledge graphs within the cultural heritage domain.
-The high ontology conformance achieved by larger LLMs demonstrates the potential for creating structurally sound CIDOC-CRM knowledge graphs automatically.
-The KBQA results indicate their utility in augmenting information retrieval.
-Future research should focus on refining ontology integration techniques, exploring benefits in complex reasoning, and evaluating scalability across diverse archives.
-The overarching aim is to leverage these technologies to significantly enhance cultural heritage data management, accessibility, and research.
+Our study contributes to the growing field exploring the synergy between LLMs, ontologies, and knowledge graphs within the cultural heritage domain.
+Our results demonstrate the potential for creating structurally sound and accurate CIDOC-CRM knowledge graphs automatically.
+However, we still notice much room for improvement in CIDOC-CRM knowledge graph evaluation methods, particularly in areas beyond the metrics measured in this study, such as entity duplication, a case where the same item appears twice in the same graph under different names.
+Future research could also explore other ontology integration techniques, refine datasets, and evaluate the scalability of these approaches across diverse archives.
+The overarching aim is to leverage these technologies to enhance cultural heritage data management, accessibility, and research.
 

### 2025-05-04 paper/paper.tex
paper: Adze graphs Qwen and R1

@@
 \usepackage[left=1.57cm,right=1.57cm,top=0.95cm,bottom=2.54cm]{geometry}
+\usepackage{graphicx}
 
@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{assets/graph-qwen3b-adze}
+    \caption{Ontology-guided graph from text "Adze" - Qwen2.5 3B}
+    \label{fig_graph_qwen3b_adze}
+\end{figure}
+
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{assets/graph-r1-adze}
+    \caption{Ontology-guided graph from text "Adze" - DeepSeek R1}
+    \label{fig_graph_r1_adze}
+\end{figure}
+
 Table \ref{tab:oc_percent} presents the ontology conformance scores for the knowledge graphs generated by the LLMs.
@@
 The results clearly illustrate a positive correlation between the parameter size of the language model and the resulting ontology conformance.
-Smaller models, such as Qwen 2.5 3B (48.63\%) and Llama 3 3B (52.28\%), demonstrated considerably low conformance rates.
-Increasing the parameter count led to improvements, as seen with Qwen 2.5 7B (50.79\%) and Llama 3 8B (63.97\%).
+Smaller models, such as Qwen 2.5 3B (48.63\%) and Llama 3 3B (52.28\%) performed with considerably low conformance rates, while increasing the parameter count led to improvements as seen with Qwen 2.5 7B (50.79\%) and Llama 3 8B (63.97\%).
+Figures \ref{fig_graph_qwen3b_adze} and \ref{fig_graph_r1_adze} visually demonstrate this difference, showing example triplets extracted from the same source text about "Adze"\footnote{https://www.museumnasional.or.id/604/}.
 
@@
 DeepSeek V3 achieved a high score of 94.6\%, and DeepSeek R1 reached an impressive \textbf{98.73\%} ontology conformance.
-This suggests that accurately interpreting and applying ontology constraints remains a considerably more challenging task for smaller language models.
+This suggests that accurately interpreting and applying ontology constraints remains a considerably more challenging task for smaller language models compared to their larger counterparts.
 

### 2025-05-04 paper/paper.tex
paper: add impact column to graphs
paper: revise IV. Results

@@
     \label{tab:qa_percent}
-    \begin{tabular}{|l|c|c|}
+    \begin{tabular}{|l|c|c|r|}
         \hline
-        Graph       & Ontology-Free               & Ontology-Guided \\
+        Graph       & Ontology-Free               & Ontology-Guided & Impact \\
         \hline
-        Blank       & \multicolumn{2}{|c|}{60.50}                   \\
+        Blank       & \multicolumn{2}{|c|}{60.50} &                          \\
         \hline
-        Qwen 2.5 3B & 73.50                       & 68.50           \\
+        Qwen 2.5 3B & 73.50                       & 68.50           & -5.00  \\
         \hline
-        Llama 3 3B  & 79.50                       & 78.00           \\
+        Llama 3 3B  & 79.50                       & 78.00           & -1.50  \\
         \hline
-        Qwen 2.5 7B & 95.50                       & 87.50           \\
+        Qwen 2.5 7B & 95.50                       & 87.50           & -8.00  \\
         \hline
-        Llama 3 8B  & 92.00                       & 90.50           \\
+        Llama 3 8B  & 92.00                       & 90.50           & -1.50  \\
         \hline
-        DeepSeek V3 & \textbf{98.00}              & \textbf{97.50}  \\
+        DeepSeek V3 & \textbf{98.00}              & \textbf{97.50}  & -0.50  \\
         \hline
-        DeepSeek R1 & 97.50                       & 95.00           \\
+        DeepSeek R1 & 97.50                       & 95.00           & -2.50  \\
         \hline
@@
     \label{tab:qa_percent_single}
-    \begin{tabular}{|l|c|c|}
+    \begin{tabular}{|l|c|c|r|}
         \hline
-        Graph       & Ontology-Free               & Ontology-Guided \\
+        Graph       & Ontology-Free               & Ontology-Guided & Impact \\
         \hline
-        Blank       & \multicolumn{2}{|c|}{62.16}                   \\
+        Blank       & \multicolumn{2}{|c|}{62.16} &                          \\
         \hline
-        Qwen 2.5 3B & 72.97                       & 67.57           \\
+        Qwen 2.5 3B & 72.97                       & 67.57           & -5.40  \\
         \hline
-        Llama 3 3B  & 80.54                       & 78.92           \\
+        Llama 3 3B  & 80.54                       & 78.92           & -1.62  \\
         \hline
-        Qwen 2.5 7B & 95.68                       & 89.19           \\
+        Qwen 2.5 7B & 95.68                       & 89.19           & -6.49  \\
         \hline
-        Llama 3 8B  & 94.05                       & 91.89           \\
+        Llama 3 8B  & 94.05                       & 91.89           & -2.16  \\
         \hline
-        DeepSeek V3 & \textbf{100}                & \textbf{98.38}  \\
+        DeepSeek V3 & \textbf{100.00}             & \textbf{98.38}  & -1.62  \\
         \hline
-        DeepSeek R1 & 98.92                       & 96.22           \\
+        DeepSeek R1 & 98.92                       & 96.22           & -2.70  \\
         \hline
@@
     \label{tab:qa_percent_multi}
-    \begin{tabular}{|l|c|c|}
+    \begin{tabular}{|l|c|c|r|}
         \hline
-        Graph       & Ontology-Free            & Ontology-Guided \\
+        Graph       & Ontology-Free            & Ontology-Guided & Impact \\
         \hline
-        Blank       & \multicolumn{2}{|c|}{40}                   \\
+        Blank       & \multicolumn{2}{|c|}{40} &                          \\
         \hline
-        Qwen 2.5 3B & 80                       & 80              \\
+        Qwen 2.5 3B & 80.00                    & 80.00           & 0.00   \\
         \hline
-        Llama 3 3B  & 66.67                    & 66.67           \\
+        Llama 3 3B  & 66.67                    & 66.67           & 0.00   \\
         \hline
-        Qwen 2.5 7B & \textbf{93.33}           & 66.67           \\
+        Qwen 2.5 7B & \textbf{93.33}           & 66.67           & -26.66 \\
         \hline
-        Llama 3 8B  & 66.67                    & 73.33           \\
+        Llama 3 8B  & 66.67                    & 73.33           & 6.66   \\
         \hline
-        DeepSeek V3 & 73.33                    & \textbf{86.67}  \\
+        DeepSeek V3 & 73.33                    & \textbf{86.67}  & 13.34  \\
         \hline
-        DeepSeek R1 & 80                       & 80              \\
+        DeepSeek R1 & 80.00                    & 80.00           & 0.00   \\
         \hline
@@
 The results of the Knowledge Base Question Answering (KBQA) task, designed to evaluate the practical utility of the generated knowledge graphs, are presented in Tables \ref{tab:qa_percent}, \ref{tab:qa_percent_single}, and \ref{tab:qa_percent_multi}.
-These tables report the overall accuracy, the accuracy on single-item questions, and the accuracy on multi-item questions, respectively, for both ontology-free and ontology-guided knowledge graphs generated by each tested LLM, in addition to the no-context "blank" test.
+These tables report the overall accuracy (n=200), the accuracy on single-item questions (n=185), and the accuracy on multi-item questions (n=15), respectively, for both ontology-free and ontology-guided knowledge graphs generated by each tested LLM, in addition to the no-context "blank" test.
+Providing any graph as context significantly improved QA performance over the blank baseline, confirming the value of extracted knowledge.
+The blank baseline's reasonable performance, especially on single-item questions, suggests the evaluator model (DeepSeek V3) possesses some inherent knowledge related to the domain.
 
-A notable observation is the relatively high performance of the "Blank" baseline across all question types, particularly on the single-item questions (62.16\% accuracy).
-This suggests that the LLMs, even without access to the generated knowledge graphs, possess a significant amount of information relevant to the Museum Nasional collection, potentially acquired during their pretraining.
-It is also possible that a subset of the questions could be answered through general reasoning capabilities without specific knowledge of the museum's data.
-The lower performance of the "Blank" baseline on multi-item questions (40\% accuracy) indicates that these more complex queries necessitate the integration of information, which the models struggle with in the absence of context.
+Consistent with the ontology conformance results, larger models generally produced graphs that lead to better KBQA scores, although the performance gap between models was less pronounced here than in the conformance task.
+This indicates that even models struggling with strict ontology adherence can still extract useful factual information.
 
-The general trend on KBQA results is that larger models tend to yield better KBQA results.
-This aligns with the findings from the ontology conformance evaluation, suggesting that increased model capacity contributes to improved information extraction and reasoning capabilities.
-However, compared to ontology conformance, the differences are not so extreme.
-This suggests that while smaller models struggle to reason around ontology constraints, they still have reasonable capability to extract information.
+Comparing the generation approaches, ontology-free graphs surprisingly led to slightly better or equal overall and single-item KBQA performance across all models.
+This suggests that for retrieving specific facts, the added structure of the ontology-guided graphs did not translate into improved accuracy in this setup, and may have even slightly hindered it in some cases.
 
-Comparing the ontology-free and guided approaches, while ontology-free graphs achieve marginally higher scores, the overall difference remains small.
-This close performance between ontology-free and ontology-guided graphs has important implications.
-It suggests that while enforcing ontological structure does not impede the extraction of answerable information, it also doesn't provide a substantial boost in question-answering accuracy, at least in this specific evaluation setting.
-This could be due to several factors, including the nature of the questions asked, the effectiveness of the ontology integration in the prompting process, or the inherent ability of the LLMs to extract relevant information even without explicit ontological guidance.
+The results for multi-item questions in particular were more varied.
+Some models benefited from ontology guidance, while others performed worse or showed no difference.
+However, conclusions drawn from this subset should be cautious due to the small number of multi-item questions (n=15).
+A larger, more diverse set of complex questions would be needed to reliably assess the impact of ontology guidance on reasoning across the graph.
+
+Overall, the KBQA results show that LLM-generated graphs enhance question answering, and larger models tend to perform better.
+However, no benefit from ontology guidance during generation for KBQA performance was consistently observed, and requires further investigation with a larger and more refined set of questions.
 

### 2025-05-04 paper/paper.tex
paper: revise abstract and conclusion

@@
 \begin{abstract}
-    The increasing volume of information in cultural heritage institutions necessitates effective knowledge management solutions.
-Knowledge graphs (KGs), particularly those aligned with ontologies like the CIDOC Conceptual Reference Model (CIDOC-CRM), offer a powerful framework for structuring and accessing this data.
+    Museum archives contain vast amounts of cultural heritage information, but accessing, integrating and analyzing this data effectively remains challenging.
+Knowledge graphs (KGs), particularly those structured according to ontologies such as the CIDOC Conceptual Reference Model (CIDOC-CRM), offer a powerful solution through semantic representation, facilitating complex queries across diverse datasets.
 However, traditional KG construction is labor-intensive.
@@
 
-    Evaluation results demonstrate that larger LLMs achieve substantially higher ontology conformance (exceeding 90\%), which is essential for ensuring semantic consistency.
-KBQA evaluation revealed a notable baseline performance by LLMs without explicit graph context, suggesting inherent knowledge.
-While graphs by larger models generally yielded higher KBQA scores, the performance difference between ontology-guided and ontology-free generated graphs was found to be marginal.
-This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the necessity for more sophisticated evaluation benchmarks to comprehensively assess CIDOC-CRM KG generation methods.
+    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle.
+While all generated KGs improved KBQA performance over a no-context baseline, the ontology-guided approach showed limited and mixed impact on KBQA accuracy compared to the ontology-free graphs in our setup.
+This research underscores the potential of LLMs for generating ontology-conformant KGs within the cultural heritage domain and highlights the need for more sophisticated evaluation benchmarks to assess CIDOC-CRM KG generation methods.
 \end{abstract}
@@
 Our results demonstrate the potential for creating structurally sound and accurate CIDOC-CRM knowledge graphs automatically.
-However, we still notice much room for improvement in CIDOC-CRM knowledge graph evaluation methods, particularly in areas beyond the metrics measured in this study, such as entity duplication, a case where the same item appears twice in the same graph under different names.
+However, we still notice much room for improvement in how we evaluate CIDOC-CRM knowledge graph generation methods, particularly in areas beyond the metrics measured in this study, such as entity duplication - the same item appearing twice in the same graph under different names.
 Future research could also explore other ontology integration techniques, refine datasets, and evaluate the scalability of these approaches across diverse archives.

### 2025-05-04 paper/paper.tex
paper: small addition to abstract

@@
 
-    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle.
+    Evaluation results show that larger models (e.g., DeepSeek R1) are capable of high ontology conformance (up to 98.73\%) while smaller models struggle to reach 50\% conformance.
 While all generated KGs improved KBQA performance over a no-context baseline, the ontology-guided approach showed limited and mixed impact on KBQA accuracy compared to the ontology-free graphs in our setup.

### 2025-05-05 paper/paper.tex
paper: et al citations

@@
 Several recent studies have explored the use of Large Language Models (LLMs) for knowledge graph generation.
-Xu et al \cite{xu2024chattf} utilize a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from textual data about Chinese traditional folklore.
-Beyond the cultural heritage domain, Van Cauter and Yakovets \cite{cauter2024ontology} demonstrate KG generation from maintenance short texts, while Carriero et al \cite{carriero2025humanevaluationofprocedural} construct KGs from procedural texts such as recipes or manuals.
+Xu et al.
+\cite{xu2024chattf} utilize a two-stage prompting method guided by an ontology derived from CIDOC-CRM to extract knowledge graph triplets from textual data about Chinese traditional folklore.
+Beyond the cultural heritage domain, Van Cauter and Yakovets \cite{cauter2024ontology} demonstrate KG generation from maintenance short texts, while Carriero et al.
+\cite{carriero2025humanevaluationofprocedural} construct KGs from procedural texts such as recipes or manuals.
 These studies often experiment with different prompting strategies to optimize the extraction process.
-In particular, Iga et al \cite{iga2024assessllm} demonstrate the impact of well-crafted prompts, specifically those employing in-context learning and chain-of-thought techniques, in yielding significant improvements.
+In particular, Iga et al.
+\cite{iga2024assessllm} demonstrate the impact of well-crafted prompts, specifically those employing in-context learning and chain-of-thought techniques, in yielding significant improvements.
 This highlights the importance of effective prompting methodologies to guide LLMs to generate accurate and consistent knowledge graphs aligned with a given ontology.
@@
 Our research focuses on the extraction of knowledge graphs from museum archives using an ontology derived from the CIDOC-CRM.
-Unlike the two-stage prompting approach employed by \cite{xu2024chattf}, we explore the effectiveness of a single-stage prompting method.
+Unlike the two-stage prompting approach employed by Xu et al.
+\cite{xu2024chattf}, we explore the effectiveness of a single-stage prompting method.
 Moreover, our study incorporates a comprehensive evaluation strategy that includes both intrinsic (ontology conformance) and extrinsic (KBQA task) metrics.

### 2025-05-05 paper/paper.tex
paper: ontology diagram
paper: specify LM Studio deployment

@@
 
+\begin{figure}[!t]
+    \centering
+    \includegraphics[width=3in]{assets/ontology}
+    \caption{CIDOC-CRM Ontology}
+    \label{fig_ontology}
+\end{figure}
+
 This study employs the CIDOC Conceptual Reference Model (CRM) to structure the knowledge graphs extracted from cultural heritage texts.
@@
         Llama 3.2 3B & Ollama on RTX 3060    \\
-        Qwen 2.5 7B  & LM Studio          \\
-        Llama 3.1 8B & LM Studio          \\
+        Qwen 2.5 7B  & LM Studio on RTX 5090 \\
+        Llama 3.1 8B & LM Studio on RTX 5090 \\
         DeepSeek V3  & DeepSeek Platform     \\

### 2025-05-05 paper/paper.tex
paper: fig ontology guided prompt
paper: figures adjustment for space, and caption

@@
 
-%\author{\small *No authors informations during review process.}
+\author{\small *No authors' information during review process.}
 % author names and affiliations
@@
 
-\begin{figure}[!t]
+\begin{figure}[t]
     \centering
-    \includegraphics[width=3in]{assets/ontology}
-    \caption{CIDOC-CRM Ontology}
+    \includegraphics[width=3.3in]{assets/ontology}
+    \caption{Ontology derived from CIDOC-CRM}
     \label{fig_ontology}
@@
 \subsubsection{Ontology-Guided}
+
+\begin{figure}[t]
+    \centering
+    \includegraphics[width=3.5in]{assets/ontology_guided}
+    \caption{Ontology-guided triplet extraction using single-stage prompting}
+    \label{fig_ontology_guided}
+\end{figure}
 
@@
     \centering
-    \caption{Models used for Knowledge Graph Generation} % Updated caption slightly
+    \caption{Models used for Knowledge Graph Generation}
     \label{tab:model_deployment}
@@
 
-\begin{figure}[!t]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=3in]{assets/graph-qwen3b-adze}
-    \caption{Ontology-guided graph from text "Adze" - Qwen2.5 3B}
+    \includegraphics[width=3.5in]{assets/graph-qwen3b-adze}
+    \caption{Graph extracted from text "Adze" with ontology - Qwen2.5 3B}
     \label{fig_graph_qwen3b_adze}
@@
 
-\begin{figure}[!t]
+\begin{figure}[h]
     \centering
-    \includegraphics[width=3in]{assets/graph-r1-adze}
-    \caption{Ontology-guided graph from text "Adze" - DeepSeek R1}
+    \includegraphics[width=3.5in]{assets/graph-r1-adze}
+    \caption{Graph extracted from text "Adze" with ontology - DeepSeek R1}
     \label{fig_graph_r1_adze}
